%==============================================================================
% Shawn M. Vuong, MD - Modern Academic CV
% Using moderncv class for professional PDF export
%==============================================================================

\documentclass[11pt, a4paper, sans]{moderncv}

%------------------------------------------------------------------------------
% Theme Options
%------------------------------------------------------------------------------
\moderncvstyle{classic}
\moderncvcolor{blue}

%------------------------------------------------------------------------------
% Character Encoding
%------------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage{T1}{fontenc}

%------------------------------------------------------------------------------
% Adjust margins
%------------------------------------------------------------------------------
\usepackage[scale=0.8]{geometry}

%------------------------------------------------------------------------------
% Personal Information
%------------------------------------------------------------------------------
\firstname{Shawn M.}
\familyname{Vuong, MD}
\title{Pediatric Neurosurgeon}
\address{1420 W 22nd St. Ste 510}{Sioux Falls, SD 57105}
\phone[mobile]{(605) 310-8163}
\email{shawn.vuong@sanfordhealth.org}
\homepage{linkedin.com/in/shawnvuong}
\social[linkedin]{shawnvuong}

%------------------------------------------------------------------------------
% Bibliography
%------------------------------------------------------------------------------
%\makeatletter
%\renewenvironment{thebibliography}[1]%
%    {%
%      \section{\refname}%
%      \small%
%      \list{\@biblabel{\@arabic\c@enumiv}}%
%           {%
%             \settowidth\labelwidth{\@biblabel{#1}}%
%             \leftmargin\labelwidth%
%             \advance\leftmargin\labelsepd%
%             \@openbib@code%
%             \usecounter{enumiv}%
%             \let\p@enumiv\@empty%
%             \renewcommand\theenumiv{\@arabic\c@enumiv}%
%           }%
%      \sloppy\clubpenalty4000\widowpenalty4000%
%      \sfcode`\.\@m%
%    }%
%    {%
%      \def\@noitemerr
%        {\@latex@warning{Empty `thebibliography' environment}}%
%      \endlist%
%    }%
%\makeatother

%------------------------------------------------------------------------------
% Publications
%------------------------------------------------------------------------------
\nocite{*}

%------------------------------------------------------------------------------
% Document
%------------------------------------------------------------------------------
\begin{document}

\makecvtitle

%------------------------------------------------------------------------------
% LICENSES
%------------------------------------------------------------------------------
\section{Licenses}
\cvitem{}{Physician Medical License (75486) -- Minnesota Board of Medical Practice, October 2023 -- August 2026}
\cvitem{}{License to Practice Medicine (20076) -- North Dakota Board of Medicine, July 2023 -- August 2026}
\cvitem{}{Permanent Medical License (MD-48008) -- Iowa Board of Medicine, November 2020 -- August 2026}
\cvitem{}{Medical License MD/DO (10990) -- South Dakota Board of Medical \& Osteopathic Examiners, July 2018 -- Present}
\cvitem{}{Interstate Medical Licensure Compact Designate -- Letter of Qualification Expiration June 2024}
\cvitem{}{Doctor of Medicine (35.122276) -- State Medical Board of Ohio, September 2013 -- October 2019}
\cvitem{}{MD Training Certification (57.021695) -- State Medical Board of Ohio, October 2012 -- June 2013}

%------------------------------------------------------------------------------
% CERTIFICATIONS
%------------------------------------------------------------------------------
\section{Certifications}

\subsection{United States Medical Licensing Exam}
\cvlistdoubleitem{USMLE Step 1 -- June 2010 (98)}{USMLE Step 2 CK -- July 2011 (98)}
\cvlistdoubleitem{USMLE Step 2 CS -- July 2011 (PASS)}{USMLE Step 3 -- February 2013 (80)}

\subsection{American Board of Neurological Surgery (ABNS)}
\cvlistdoubleitem{Written Exam -- March 2016 (PASS)}{Oral Exam -- May 2022 (PASS)}
\cvlistdoubleitem{Diplomate -- May 2022, Certificate \#220543118}{Recognition of Focused Practice -- Pediatrics}

\subsection{American Board of Pediatric Neurosurgery (ABPNS)}
\cvlistdoubleitem{Subspecialty Exam -- June 2019 (PASS)}{Oral Board Exam -- May 2022 (PASS)}
\cvitem{}{Diplomate -- June 2023, Certificate \#220543118}

%------------------------------------------------------------------------------
% EDUCATION
%------------------------------------------------------------------------------
\section{Education}

\cventry%
  {Fellow in Pediatric Neurosurgery}%
  {Cincinnati Children's Hospital Medical Center}%
  {Cincinnati, OH}%
  {July 2018 -- July 2019}%
  {Division of Neurosurgery \textbullet{} U.S. News \& World Report 2nd Best Children's Hospital 2018-2019 \textbullet{} Fellowship Director: Francesco T. Mangano}

\cventry%
  {Chief Resident in Neurosurgery}%
  {University of Cincinnati Medical Center}%
  {Cincinnati, OH}%
  {July 2017 -- June 2018}%
  {Department of Neurosurgery \textbullet{} Chairmen: Joseph C. Cheng \& Mario Zuccarello}

\cventry%
  {Resident in Neurosurgery}%
  {University of Cincinnati Medical Center}%
  {Cincinnati, OH}%
  {July 2012 -- June 2018}%
  {Department of Neurosurgery -- Mayfield Clinic \& Cincinnati Children's Hospital Medical Center \textbullet{} Over 1500 logged surgical cases \textbullet{} Experience with minimally invasive spine, open complex spine, stereotactic radiosurgery, endovascular neurosurgery, open vascular, trauma, peripheral nerve, skull-base, tumor, deep brain stimulation, epilepsy, and pediatrics}

\cventry%
  {Medical Doctorate (MD)}%
  {Sanford School of Medicine, University of South Dakota}%
  {Sioux Falls, SD}%
  {August 2008 -- May 2012}%
  {Student of the Yankton Model Program \textbullet{} Over 1300 logged patient encounters \textbullet{} Over 250 logged surgical cases (most first assist)}

\cventry%
  {Bachelor of Science (BS), Biology, Summa Cum Laude}%
  {University of South Dakota}%
  {Vermillion, SD}%
  {September 2004 -- May 2008}%
  {}

%------------------------------------------------------------------------------
% PROFESSIONAL APPOINTMENTS \& EMPLOYMENT
%------------------------------------------------------------------------------
\section{Professional Appointments \& Employment}

\cventry%
  {Chief of Surgery, Sanford Medical Center}%
  {Sanford Health}%
  {Sioux Falls, SD}%
  {July 2022 -- Present}%
  {Surgical Operations \textbullet{} Oversee credentials and privileges for all surgical physicians, APPs, and assistants \textbullet{} Oversee over 138 surgeons, over 200 total OR staff, 45 full-time operating rooms \textbullet{} Lead and organized block scheduling initiative to increase efficiencies in the OR flow and schedule \textbullet{} Provided guidance regarding CRNA work shortage and leadership changes \textbullet{} Supervising physician for OR Advance Practice Providers}

\cventry%
  {Staff Neurosurgeon}%
  {Sanford Medical Center}%
  {Sioux Falls, SD}%
  {August 2019 -- Present}%
  {Department of Surgery, Division of Neurosurgery}

\cventry%
  {Chair of Neurosurgery}%
  {Sanford Health Sioux Falls}%
  {Sioux Falls, SD}%
  {October 2022 -- Present}%
  {Volume review, efficiency review, peer review, and department efficiencies \textbullet{} Lead and represent neurosurgery department \textbullet{} In collaboration with the department director, responsible for achieving quality, SAFE, and operational goals \textbullet{} Recruited 3 additional neurosurgeons and helped rebuild the department \textbullet{} Lead monthly department meetings \textbullet{} Oversee 4 full-time and 2 part-time surgeons as well as any locums coverage and 7 APPs}

\cventry%
  {Assistant Professor of NeuroSciences}%
  {Sanford School of Medicine, University of South Dakota}%
  {Sioux Falls, SD}%
  {November 2020 -- Present}%
  {Department of Neurosciences \textbullet{} Sponsor medical students for the student chapter of the AANS}

\cventry%
  {Assistant Professor of Surgery}%
  {Sanford School of Medicine, University of South Dakota}%
  {Sioux Falls, SD}%
  {August 2019 -- Present}%
  {Department of Surgery}

\cventry%
  {Instructor of Neurosurgery}%
  {University of Cincinnati Medical Center}%
  {Cincinnati, OH}%
  {July 2012 -- June 2018}%
  {Department of Neurosurgery -- Mayfield Clinic \& Cincinnati Children's Hospital Medical Center}

\cventry%
  {Surgery Tech Program Advisory Board -- Surgeon Liaison}%
  {Southeast Technical Institute}%
  {Sioux Falls, SD}%
  {May 2025 -- Present}%
  {Provide surgeon input for STI's surgical technician education program \textbullet{} ARC/STSA accredited advisory board}

\cventry%
  {Chief of Surgery \& Neurosurgery Liaison}%
  {Surgical Operations Committee, Sanford Health Sioux Falls}%
  {Sioux Falls, SD}%
  {November 2021 -- Present}%
  {Volume review, efficiency review, value analysis, surgical block time request review \textbullet{} Lead and represent surgeons, working with administration to review and improve surgical operations \textbullet{} Lead peer review meeting for continued commitment to patient quality and safety \textbullet{} Lead the overall of surgical block time request criteria and protocols (March 2023) \textbullet{} Performed Biannual Surgeon scorecard reviews (via Statit)}

\cventry%
  {Neurosurgery Liaison}%
  {Trauma Quality \& Safety Committee, Sanford Health Sioux Falls}%
  {Sioux Falls, SD}%
  {September 2019 -- Present}%
  {Review both adult and pediatric trauma protocols \textbullet{} Assist in providing peer-review of adult and pediatric trauma cases}

\cventry%
  {Neurosurgery Liaison}%
  {Surgery Case Review Committee, Sanford Health Sioux Falls}%
  {Sioux Falls, SD}%
  {March 2021 -- Present}%
  {Assist in providing peer-review for both adult and pediatric non-trauma surgical cases \textbullet{} Discuss and implement systemic surgical protocols to provide safer surgery for patients}

%------------------------------------------------------------------------------
% AWARDS, HONORS, \& GRANTS
%------------------------------------------------------------------------------
\section{Awards, Honors, \& Grants}

\cvitem{Key to the Castle Winner}{December 2022}

\cvitem{Always Available Award}{Awarded for always being amiable for pediatric neurosurgery opinions and recommendations despite not being on call. Nominated by Dr. Kellie Sweet}

\cvitem{Frank H. Mayfield Society}{Inducted April 14, 2018 -- Mayfield Brain \& Spine -- Graduate of the University of Cincinnati Neurosurgery Residency}

\cvitem{Hydrocephalus Association's Young Investigator 2018 Travel Award}{January 2018 -- Cincinnati Children's Hospital \& Medical Center, University of Cincinnati Medical Center, \& the Mayfield Clinic -- Poster: CRISPR/Cas9-Based Development of progressive hydrocephaly (prh) Rat Model -- Awarded funding to attend HACONNECT'18}

\cvitem{2017 Hydrocephalus Association Award}{December 2017 -- Resident award for the best presentation on Hydrocephalus at the 2017 AANS/CNS Joint Pediatric Section Annual Meeting, Houston, TX -- Presented at AANS 2018, New Orleans, LA -- Presentation: CRISPR/Cas9-Based Development of progressive hydrocephaly (prh) Rat Model of Hydrocephalus}

\cvitem{Mayfield Education \& Research Foundation (MERF) Grant}{\$48,000 -- January 2016 -- Cincinnati Children's Hospital \& Medical Center, University of Cincinnati Medical Center, \& the Mayfield Clinic -- Research: Identification of Molecular Therapeutic Targets in Choroid Plexus using a Novel Mouse Model of Communicating Hydrocephalus}

%------------------------------------------------------------------------------
% PROFESSIONAL MEMBERSHIPS
%------------------------------------------------------------------------------
\section{Professional Memberships}
\cvlistdoubleitem{American College of Surgeons (ACS) -- Fellow}{International College of Surgeons (ICS) -- Fellow}
\cvlistdoubleitem{American Association of Neurological Surgeons (AANS) -- Fellow}{Congress of Neurological Surgeons (CNS) -- Fellow}
\cvlistdoubleitem{AANS/CNS Section on Pediatric Neurological Surgery -- Member}{The American Academy of Neurological \& Orthopaedic Surgeons -- Honorary Member}

%------------------------------------------------------------------------------
% RESEARCH \& TEACHING EXPERIENCE
%------------------------------------------------------------------------------
\section{Research \& Teaching Experience}

\cventry%
  {Member of Ph.D. Dissertation Committee}%
  {University of South Dakota Sanford School of Medicine}%
  {Sioux Falls, SD}%
  {September 2025 -- Present}%
  {Dissertation committee for Tana Lick, MD/PhD Candidate 2029}

\cvitem{Outstanding Mentor Award}{April 2022 -- University of South Dakota Sanford School of Medicine -- Awarded by the medical school class of 2022 to a mentor who was a senior students most influential mentor. Awarded by Nicholas Pekas, MD, PhD, class of 2022}

\cventry%
  {Resident Physician Researcher}%
  {Cincinnati Children's Hospital \& Medical Center}%
  {Cincinnati, OH}%
  {July 2016 -- June 2017}%
  {Neuroscience research on congenital hydrocephalus in a mouse model under the supervision of June Goto Nakamura Ph.D. and Francesco Mangano, DO}

\cventry%
  {Research Technician}%
  {University of South Dakota}%
  {Vermillion, SD}%
  {January 2006 -- July 2010}%
  {Addiction pathways neuroscience research conducted under the supervision of Gina L. Forster Ph.D.}

\cventry%
  {Emergency Medical Technician -- Instructor}%
  {Vermillion/Clay County EMS}%
  {Vermillion, SD}%
  {July 2005 -- July 2010}%
  {NREMT-Basic certification received May 2005, and NREMT-Intermediate 85 received June 2007 \textbullet{} Taught EMT-Basic students, human anatomy \& physiology, vital signs, SAMPLE history taking, pharmacology, respiratory system, cardiac system, and the recognition and treatment of bleeding and shock as an EMT instructor}

%------------------------------------------------------------------------------
% PUBLICATIONS
%------------------------------------------------------------------------------
\section{Publications}
\textit{Peer-Reviewed Journal Articles}

\nocite{*}
\bibliographystyle{plain}
\bibliography{publications}

%------------------------------------------------------------------------------
% CONFERENCE ACTIVITY \& PRESENTATIONS
%------------------------------------------------------------------------------
\section{Conference Activity \& Presentations}

\subsection{2026}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. Pillar 1 - First Year Medical Students - Neuro-Block Clinical Correlation. Sanford School of Medicine, University of South Dakota. Vermillion, SD.}

\subsection{2025}
\cvitem{}{Vuong SM. The Road to Neurosurgery: The Pre-Med Seminar. University of South Dakota Pre-Med Seminar Course. Vermillion, SD.}
\cvitem{}{Vuong SM. Inter-ventricular Hemorrhage of Prematurity. South Dakota Neuro-Stroke Conference 2025 - American Heart Association. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. Pillar 1 - First Year Medical Students - Neuro-Block Clinical Correlation. Sanford School of Medicine, University of South Dakota. Vermillion, SD.}
\cvitem{}{Vuong SM. Advanced Provider Session: Burst Fracture \& Anterior Column Support with Stryker Spine Jack. The Winter Clinics for Cranial and Spinal Surgery. Snowmass, CO.}
\cvitem{}{Vuong SM. What the hell does a neurosurgeon know about sales? Aesculap 2025 National Sales Meeting - Neuro Division. Austin, TX.}

\subsection{2024}
\cvitem{}{Vuong SM. Brain Death - A Clinician's Perspective. The 2024 Alumni Speaker. Center for Brain and Behavior Research (CBBRe) 2024 Symposium on Neurotics \& Bioethics. Vermillion, SD.}
\cvitem{}{Vuong SM \& Opoku-Darko M. Intracerebral Hemorrhage - Neurosurgery's role. Neurosurgery Department Lunch \& Learn. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Spinal Fracture Review. Neurosurgery Department Lunch \& Learn. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Advanced Provider Session: Spinal Fracture Review. The Winter Clinics for Cranial and Spinal Surgery. Snowmass, CO.}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. Pillar 1 - First Year Medical Students - Neuro-Block Clinical Correlation. Sanford School of Medicine, University of South Dakota. Vermillion, SD.}
\cvitem{}{Vuong SM. Basivertebral Nerve Ablation. Sanford Chiropractic Symposium. Sioux Falls, SD.}
\cvitem{}{Vuong SM. The Six Chiaris. South Dakota Academy of Family Physicians Winter Seminar. Deadwood, SD.}
\cvitem{}{Vuong SM. Pediatric Neurosurgery - Lunch and Learn. Pediatrics Department, Sanford Health. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. Anesthesia Department Monthly Education. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Spinal Fracture Review. The Sanford EMS Refresher Course. Sioux Falls, SD.}

\subsection{2023}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. The Surgical Staff In-Service. Sanford Health. Sioux Falls, SD.}
\cvitem{}{Vuong SM. Advanced Provider Session: Spinal Cord Stimulator Review. The Winter Clinics for Cranial and Spinal Surgery. Snowmass, CO.}
\cvitem{}{Vuong SM. Craniotomy for Severe Traumatic Brain Injury. The Sanford EMS Refresher Course. Virtual Symposium. Sioux Falls, SD.}

%------------------------------------------------------------------------------
% (Presentations continue in similar format...)
%------------------------------------------------------------------------------

%------------------------------------------------------------------------------
% COURSES \& MEETINGS
%------------------------------------------------------------------------------
\section{Courses \& Meetings}
\cvlistdoubleitem{Aesculap Academy. Hydrocephalus Management Course. Nov 2025. Miami, FL.}{2024 AANS/CNS Section on Pediatric Neurological Surgery. Dec 2024. New York City, NY.}
\cvlistdoubleitem{ACS South Dakota and North Dakota Chapters 2024 Annual Meeting. Apr 2024.}{Relievant Intracept Training Course. Nov 2023. Nashville, TN.}
\cvlistdoubleitem{Aesculap Academy. Hydrocephalus Management Course. Oct 2023. Pittsburgh, PA.}{Stryker Navigation VIP visit. Oct 2022. Washington, DC.}

%------------------------------------------------------------------------------
% PATENTS
%------------------------------------------------------------------------------
\section{Patents}
\cvitem{}{Vuong SM. Ocular Shield for Facilitating Generation of Visual Evoked Potentials (VEP). \textit{U.S. Patent 11,147,712}. October 19, 2021.}

%------------------------------------------------------------------------------
% OTHER VENTURES
%------------------------------------------------------------------------------
\section{Other Ventures}
\cventry%
  {Ordained Minister}%
  {Universal Life Church}%
  {}{April 2025 -- Present}%
  {Performed a wedding ceremony August 30, 2025}

\cventry%
  {Partner}%
  {Frontline Development}%
  {Sioux City, IA}%
  {July 2025 -- Present}%
  {Real estate and development projects \textbullet{} Board of Directors for the building, development, and operations of Siouxland Splash}

\end{document}
